---
title: "Team Name Analysis"
author: "Brian Waismeyer"
date: "October 20, 2015"
output: html_document
---

This is an analysis of Team 7's "Team Name and Logo" survey data. These data
were collected in a highly scientific manner and can be considered an exact
reading of the team's feelings towards different candidate names and towards
Amanda's logo skillz.

## Load Libraries and Data

First off, we need to load the most powerful R packages possible - the scale
and importance of the data is nearly beyond comprehension.

```{r, results='hold', message=FALSE, warning=FALSE}
# load crazy-powerful packages
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
```

Then we need to lovingly, cautiously, and tremendously load the data.

```{r, results='hold'}
# load the data, assuming that data is in the current working directory
team_df <- read.csv("Score the team names! (Responses) - Form Responses 1.csv",
                    stringsAsFactors = FALSE)

# ignoring the stupid formatting warning, we inspect the results
str(team_df)
```

## Carpenter the Data

The data arrives in a format as wide as yo mama and with more awkward periods.
With calm strokes and sturdy hands, we craft the data to be lean and mean and
clean.

```{r, results='hold'}
# rename the last two variables to be less crazy
names(team_df)[16:17] <- c("notes", "Amanda_logo")

# grab the data by the hand
clean_df <- team_df %>%
    # drop notes and timestamp because we don't care
    select(-notes, -Timestamp) %>%
    # add a person id 'cuz it's easier to deal with than the timestamps
    mutate(person_id = row_number()) %>%
    # flip the data from wide as #### to long
    gather("team_name", "rating", -person_id, -Amanda_logo)

# clean up all those cray-cray periods
clean_df$team_name <- str_replace_all(clean_df$team_name, "[.]", " ")

# replace double spaces with sweet, sweet space-dash-space
clean_df$team_name <- str_replace_all(clean_df$team_name, "[ ][ ]", " - ")

# ADMIRE OUR WORK
tbl_df(clean_df)
```

## Stare Deep into the Data's Eyes

We have carved ourselves a unicorn. Let's pet that unicorn and see what wishes
it grants us. 

First we check out our thoughts on team names.

```{r, results='hold'}
# get the mean/sd for each team name rating and rank the names by sexy
clean_df %>%
    group_by(team_name) %>%
    summarise(mean_rating = mean(rating),
              sd_rating = sd(rating)) %>%
    arrange(desc(mean_rating), 
            desc(sd_rating))

# slap it into a graph BECAUSE WE CAN
clean_df %>%
    group_by(team_name) %>%
    summarise(mean_rating = mean(rating),
              sd_rating = sd(rating)) %>%
    ggplot(aes(x = team_name, y = mean_rating)) +
        geom_bar(stat = "identity") +
        theme(axis.text.x=element_text(angle = -90, hjust = 0))
```

Those are some sexy thoughts for some sexy team names.

Next we assess Amanda's logo skilllllllzzz.

```{r, results='hold'}
# table it
clean_df %>%
    group_by(Amanda_logo, person_id) %>%
    summarise() %>%
    summarise(answer_count = n()) %>%
    ungroup() %>%
    mutate(answer_prop = answer_count / sum(answer_count))

# we don't need  no graph to see what we need to see
```

Mmm. It seems that Evil Amanda should be in charge of everything.

Finally, we grapple with Amanda's demand for a scatterplot by plotting the
weirdest things that come to mind.

```{r, results='hold'}
# first we plot mean rating against sd rating to see how variability changes
# as mean ratings approach different regions of the rating range...
# that's probably the smartest thing I've written in this whole report...
# I'm gonna smugly congratulate myself for this all day...
clean_df %>%
    group_by(team_name) %>%
    summarise(mean_rating = mean(rating),
              sd_rating = sd(rating)) %>%
    ggplot(aes(x = mean_rating, y = sd_rating)) +
        geom_point() +
        # we slap on a smoother to make it look like cool stuff is happening
        geom_smooth()

# next we assess if people who rate spandex names low rate everything low,
# implying that spandex-repressed people are h8ters
clean_df %>%
    # need a column to distinguish types of team name
    mutate(spandex_name = ifelse(grepl("Spandex", team_name),
                                 "spandex_infused", "spandex_less")) %>%
    # get each persons mean rating for spandex and non-spandex titles
    group_by(person_id, spandex_name) %>%
    summarise(mean_rating = mean(rating)) %>%
    # spread the dataframe so that we can make points
    spread(spandex_name, mean_rating) %>%
    # make us a PLOT
    ggplot(aes(x = spandex_infused, y = spandex_less)) +
        geom_point()
    
```

We learn that our group is pretty small to make scatterplots and Bibin is
totally a negative-spandex-Nancy.